\LARGE Micro- versus meso-scale population models for ecological forecasting under climate change

### 2014-12-04 manuscript/ms_MicroMeso.Rnw
ms updates
added deviance and coefficient figures for climate effects

<<echo=FALSE, include=FALSE, fig=TRUE, label=DevFig, width=4, height=3>>=
library(ggplot2)
devGQ <- data.frame(VitalRate = c("Growth", "Survival", "Colonization"),
                       ConstantModel = rep(NA,3),
                       ClimateModel = rep(NA,3),
                       FullModel = rep(NA,3),
                       ClimateContribution = rep(NA,3))
devGQ$FullModel[1] <- round(read.csv("../montana/ipm/vitalRateRegs/growth/growthDeviance.csv")[,2],2)
devGQ$ClimateModel[1] <- round(read.csv("../montana/ipm/vitalRateRegs/growth/growthDevianceCLIMATE.csv")[,2],2)
devGQ$ConstantModel[1] <- round(read.csv("../montana/ipm/vitalRateRegs/growth/growthDevianceCONSTANT.csv")[,2],2)
devGQ$FullModel[2] <- round(read.csv("../montana/ipm/vitalRateRegs/survival/survivalDeviance.csv")[,2],2)
devGQ$ClimateModel[2] <- round(read.csv("../montana/ipm/vitalRateRegs/survival/survivalDevianceCLIMATE.csv")[,2],2)
devGQ$ConstantModel[2] <- round(read.csv("../montana/ipm/vitalRateRegs/survival/survivalDevianceCONSTANT.csv")[,2],2)
devGQ$FullModel[3] <- round(read.csv("../montana/ipm/vitalRateRegs/recruitment/recruitmentDeviance.csv")[,2],2)
devGQ$ClimateModel[3] <- round(read.csv("../montana/ipm/vitalRateRegs/recruitment/recruitmentDevianceCLIMATE.csv")[,2],2)
devGQ$ConstantModel[3] <- round(read.csv("../montana/ipm/vitalRateRegs/recruitment/recruitmentDevianceCONSTANT.csv")[,2],2)
devGQ$ClimateContribution[1] <- with(devGQ[1,], (ClimateModel-ConstantModel)/(FullModel-ConstantModel))
devGQ$ClimateContribution[2] <- with(devGQ[2,], (ConstantModel-ClimateModel)/(ConstantModel))
devGQ$ClimateContribution[3] <- with(devGQ[3,], (ConstantModel-ClimateModel)/(ConstantModel))

@@

<<echo=FALSE, include=FALSE, fig=TRUE, label=CoefFig, width=8.5, height=8>>=
gQC <- read.csv("../montana/quadBM/vitalRateRegressions/growth/growthQuants.csv")
gQC <- gQC[129:144,]
coefNames <- c("ppt1", "ppt2", "temp1", "temp2")
gQC$X <- rep(coefNames, each=4)
gQC$rate <- "growth"
sQC <- read.csv("../montana/quadBM/vitalRateRegressions/survival/survivalQuants.csv")
sQC <- sQC[33:48,]
coefNames <- c("ppt1", "ppt2", "temp1", "temp2")
sQC$X <- rep(coefNames, each=4)
sQC$rate <- "survival"
rQC <- read.csv("../montana/quadBM/vitalRateRegressions/colonization/colonizationQuants.csv")
rQC <- rQC[29:44,]
coefNames <- c("ppt1", "ppt2", "temp1", "temp2")
rQC$X <- rep(coefNames, each=4)
rQC$rate <- "colonization"
plotQC <- rbind(gQC,sQC,rQC)
gQ <- ggplot(plotQC, aes(x=species, y=X50., color=rate))+
  geom_hline(aes(yintercept=0), linetype="dashed")+
  geom_errorbar(aes(ymin=X2.5., ymax=X97.5.), width=0, position=position_dodge(width=0.5))+
  geom_errorbar(aes(ymin=X25., ymax=X75.), width=0, size=1.5, position=position_dodge(width=0.5))+
  geom_point(size=4, position=position_dodge(width=0.5))+
  facet_grid(X~.)+
  coord_flip()+
  theme_bw()+
  guides(color=FALSE)

gIC <- read.csv("../montana/ipm/vitalRateRegs/growth/growthQuants.csv")
gIC <- gIC[133:148,]
coefNames <- c("ppt1", "ppt2", "temp1", "temp2")
gIC$X <- rep(coefNames, each=4)
gIC$rate <- "growth"
sIC <- read.csv("../montana/ipm/vitalRateRegs/survival/survivalQuants.csv")
sIC <- sIC[133:148,]
coefNames <- c("ppt1", "ppt2", "temp1", "temp2")
sIC$X <- rep(coefNames, each=4)
sIC$rate <- "survival"
rIC <- read.csv("../montana/ipm/vitalRateRegs/recruitment/recruitmentQuants.csv")
rIC <- rIC[81:96,]
coefNames <- c("ppt1", "ppt2", "temp1", "temp2")
rIC$X <- rep(coefNames, each=4)
rIC$rate <- "colonization"
plotIC <- rbind(gIC,sIC,rIC)
gI <- ggplot(plotIC, aes(x=species, y=X50., color=rate))+
  geom_hline(aes(yintercept=0), linetype="dashed")+
  geom_errorbar(aes(ymin=X2.5., ymax=X97.5.), width=0, position=position_dodge(width=0.5))+
  geom_errorbar(aes(ymin=X25., ymax=X75.), width=0, size=1.5, position=position_dodge(width=0.5))+
  geom_point(size=4, position=position_dodge(width=0.5))+
  facet_grid(X~.)+
  coord_flip()+
  theme_bw()+
  guides(color=FALSE)

@@

\begin{figure}[th!]
\begin{center}
\includegraphics{Fig-CoefFig}
\end{center}
\caption{Posterior means (points), 75\% credible intervals (heavy lines), and 95\% credible intervals (light lines) of climate effects in each vital rate statistical model. The quadrat level estimates are shown in left panels and individual level estimates are in right panels. Color codes: blue = colonization/recruitment, green = growth, red = survival.}
\label{fig:CoefFig}
\end{figure}

>>>>

<<echo=FALSE, include=FALSE, fig=TRUE, label=DevFig, width=5, height=3, results=hide>>=
library(ggplot2)
devGQ <- data.frame(VitalRate = c("Growth", "Survival", "Colonization"),
                       ConstantModel = rep(NA,3),
                       ClimateModel = rep(NA,3),
                       FullModel = rep(NA,3),
                       ClimateContribution = rep(NA,3))
devGQ$FullModel[1] <- round(read.csv("../montana/ipm/vitalRateRegs/growth/growthDeviance.csv")[,2],2)
devGQ$ClimateModel[1] <- round(read.csv("../montana/ipm/vitalRateRegs/growth/growthDevianceCLIMATE.csv")[,2],2)
devGQ$ConstantModel[1] <- round(read.csv("../montana/ipm/vitalRateRegs/growth/growthDevianceCONSTANT.csv")[,2],2)
devGQ$FullModel[2] <- round(read.csv("../montana/ipm/vitalRateRegs/survival/survivalDeviance.csv")[,2],2)
devGQ$ClimateModel[2] <- round(read.csv("../montana/ipm/vitalRateRegs/survival/survivalDevianceCLIMATE.csv")[,2],2)
devGQ$ConstantModel[2] <- round(read.csv("../montana/ipm/vitalRateRegs/survival/survivalDevianceCONSTANT.csv")[,2],2)
devGQ$FullModel[3] <- round(read.csv("../montana/ipm/vitalRateRegs/recruitment/recruitmentDeviance.csv")[,2],2)
devGQ$ClimateModel[3] <- round(read.csv("../montana/ipm/vitalRateRegs/recruitment/recruitmentDevianceCLIMATE.csv")[,2],2)
devGQ$ConstantModel[3] <- round(read.csv("../montana/ipm/vitalRateRegs/recruitment/recruitmentDevianceCONSTANT.csv")[,2],2)
devGQ$ClimateContribution[1] <- with(devGQ[1,], (ClimateModel-ConstantModel)/(FullModel-ConstantModel))
devGQ$ClimateContribution[2] <- with(devGQ[2,], (ConstantModel-ClimateModel)/(ConstantModel))
devGQ$ClimateContribution[3] <- with(devGQ[3,], (ConstantModel-ClimateModel)/(ConstantModel))

@@

<<echo=FALSE, include=FALSE, fig=TRUE, label=CoefFig, width=8.5, height=10, results=hide>>=
gQC <- read.csv("../montana/quadBM/vitalRateRegressions/growth/growthQuants.csv")
gQC <- gQC[129:144,]
coefNames <- c("ppt1", "ppt2", "temp1", "temp2")
gQC$X <- rep(coefNames, each=4)
gQC$rate <- "growth"
sQC <- read.csv("../montana/quadBM/vitalRateRegressions/survival/survivalQuants.csv")
sQC <- sQC[33:48,]
coefNames <- c("ppt1", "ppt2", "temp1", "temp2")
sQC$X <- rep(coefNames, each=4)
sQC$rate <- "survival"
rQC <- read.csv("../montana/quadBM/vitalRateRegressions/colonization/colonizationQuants.csv")
rQC <- rQC[29:44,]
coefNames <- c("ppt1", "ppt2", "temp1", "temp2")
rQC$X <- rep(coefNames, each=4)
rQC$rate <- "colonization"
plotQC <- rbind(gQC,sQC,rQC)
gQ <- ggplot(plotQC, aes(x=species, y=X50., color=rate))+
  geom_hline(aes(yintercept=0), linetype="dashed")+
  geom_errorbar(aes(ymin=X2.5., ymax=X97.5.), width=0, position=position_dodge(width=0.5))+
  geom_errorbar(aes(ymin=X25., ymax=X75.), width=0, size=1.5, position=position_dodge(width=0.5))+
  geom_point(size=4, position=position_dodge(width=0.5))+
  ylab("Standardized Coefficient Value")+
  xlab("Species")+
  facet_grid(X~.)+
  coord_flip()+
  theme_bw()+
  scale_color_manual(values=c("grey25", "steelblue", "slateblue"))+
  guides(color=guide_legend(title=""))+
  theme(legend.position="top")

gIC <- read.csv("../montana/ipm/vitalRateRegs/growth/growthQuants.csv")
gIC <- gIC[133:148,]
coefNames <- c("ppt1", "ppt2", "temp1", "temp2")
gIC$X <- rep(coefNames, each=4)
gIC$rate <- "growth"
sIC <- read.csv("../montana/ipm/vitalRateRegs/survival/survivalQuants.csv")
sIC <- sIC[133:148,]
coefNames <- c("ppt1", "ppt2", "temp1", "temp2")
sIC$X <- rep(coefNames, each=4)
sIC$rate <- "survival"
rIC <- read.csv("../montana/ipm/vitalRateRegs/recruitment/recruitmentQuants.csv")
rIC <- rIC[81:96,]
coefNames <- c("ppt1", "ppt2", "temp1", "temp2")
rIC$X <- rep(coefNames, each=4)
rIC$rate <- "colonization"
plotIC <- rbind(gIC,sIC,rIC)
gI <- ggplot(plotIC, aes(x=species, y=X50., color=rate))+
  geom_hline(aes(yintercept=0), linetype="dashed")+
  geom_errorbar(aes(ymin=X2.5., ymax=X97.5.), width=0, position=position_dodge(width=0.5))+
  geom_errorbar(aes(ymin=X25., ymax=X75.), width=0, size=1.5, position=position_dodge(width=0.5))+
  geom_point(size=4, position=position_dodge(width=0.5))+
  ylab("Standardized Coefficient Value")+
  xlab("Species")+
  facet_grid(X~.)+
  coord_flip()+
  theme_bw()+
  scale_color_manual(values=c("grey25", "steelblue", "slateblue"))+
#   guides(color=FALSE)+
  guides(color=guide_legend(title=""))+
  theme(legend.position="top")

@@

\begin{figure}[th!]
\begin{center}
\includegraphics[ width=\textwidth] {Fig-CoefFig}
\end{center}
\caption{Posterior means (points), 75\% credible intervals (heavy lines), and 95\% credible intervals (light lines) of climate effects in each vital rate statistical model. The quadrat level estimates are shown in left panels and individual level estimates are in right panels.}
\label{fig:CoefFig}
\end{figure}
